Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
hop

The analysis of linear equalities (PKEQ) performs very fast compared
to other abstract domains, but yields very imprecise invariants:
it only detects relations of the form $\sum a_i x_i = C$ where $a_i$ and $C$ are constants.
The comparison between the domain of convex polyhedra and linear congruences
shows the percentage of points where the use of congruences refines the
invariant. This is the case for $1.04\%$ of the control points in $P_R$.
\DM{Je croyais qu'on ne pouvait pas utiliser PPLGRID?}

>>>>

The analysis of linear equalities (PKEQ) performs very fast compared
to other abstract domains, but yields very imprecise invariants:
it only detects relations of the form $\sum_i a_i x_i = C$ where $a_i$ and $C$ are constants.
The comparison between the domain of convex polyhedra and linear congruences
shows the percentage of points where the use of congruences refines the
invariant. This is the case for $1.04\%$ of the control points in $P_R$.
\DM{Je croyais qu'on ne pouvait pas utiliser PPLGRID?}
